Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-26 manuscript/manuscript.Rmd
updates fig 1 with multipanel

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Time series of average percent cover of our four focal species: *Bouteloua gracilis* (BOGR), *Hesperostipa comata* (HECO), *Pascopyrum smithii* (PASM), and *Poa secunda* (POSE).", fig.height=4}
obs_data <- read.csv("../analysis/speciesData/quadAllCover.csv")
#remove zeros for averaging
obs_data <- obs_data[which(obs_data$propCover>0),]
avgobs <- ddply(obs_data, .(year, Species), summarise,
                mean_cover = mean(propCover))
ggplot(avgobs, aes(x=(1900+year), y=mean_cover*100, shape=Species, linetype=Species))+
  geom_line()+
  geom_point(size=5, color="white")+
  geom_point(size=3)+
  ylab("Mean cover (%)")+
  xlab("Year")+
  theme_bw()
```

>>>>

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Time series of average percent cover over all quadrats for our four focal species: *Bouteloua gracilis* (BOGR), *Hesperostipa comata* (HECO), *Pascopyrum smithii* (PASM), and *Poa secunda* (POSE). Light grey lines show trajectories of individual quadrats. Note the different y-axis scales across panels.", fig.height=3, fig.width=8.5}
obs_data <- read.csv("../analysis/speciesData/quadAllCover.csv")
#remove zeros for averaging
obs_data <- obs_data[which(obs_data$propCover>0),]
avgobs <- ddply(obs_data, .(year, Species), summarise,
                mean_cover = mean(propCover))

ggplot()+
  geom_line(data = obs_data, aes(x=(1900+year), y=propCover*100, group=quad), 
            color="grey", size=0.25)+
  geom_line(data=avgobs, aes(x=(1900+year), y=mean_cover*100))+
  geom_point(data=avgobs, aes(x=(1900+year), y=mean_cover*100),size=3)+
  ylab("Mean cover (%)")+
  xlab("Year")+
  theme_bw()+
  facet_wrap("Species", ncol=4, nrow=1, scales = "free")+
  guides(shape=FALSE, linetype=FALSE)
```

### 2015-06-26 manuscript/manuscript.tex
updates fig 1 with multipanel

\section{Do we need detailed demographic data to forecast the impacts of
climate change on
populations?}\label{do-we-need-detailed-demographic-data-to-forecast-the-impacts-of-climate-change-on-populations}

@@

Our demographic data comes from the Fort Keogh Livestock and Range
Research Laboratory in eastern Montana's northern mixed prairie near
Miles City, Montana, USA ($46^{\circ}$ 19' N, $105^{\circ}$ 48' W). The
dataset is freely available on Ecological Archives\footnote{\url{http://esapubs.org/archive/ecol/E092/143/}}
(Anderson et al. 2011) , and interested readers should refer to the
metadata therein for a complete description. The site is about 800 m
above sea level and mean annual precipitation (1878-2009) is 334 mm,
with most annual precipitation falling from April through September. The
site is grass dominated and, for the purposes of our study, we focus on
the four most abundant graminoid species: \emph{Bouteloua gracilis}
(BOGR), \emph{Hesperostipa comata} (HECO), \emph{Pascopyrum smithii}
(PASM), and \emph{Poa secunda} (POSE).

@@

In this paper, we model populations based on two levels of data:
individual and quadrat (Fig. 1). The individual data is the ``raw''
data. For the quadrat level we data we simply sum individual areal cover
for each quadrat by species. This is equivalent to a perfect census of
quadrat percent cover, so we do not need to consider measurement error.
Based on these two datasets we can compare population models built using
individual level data and aggregated quadrat level data.

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Work flow of the data aggregation, model fitting, and
population simulating.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Proportional change in species' mean cover caused by a 1\%
increase in observed precipitation (+ppt), temperature (+temp), or both
(+ppt\&temp) as predicted by the individual-based IPM and the
aggregate-based QBM. Top panels show the mean predicted proportional
change in cover; lower panels show the 90\% quantiles of predicted
proportional cover change. Mean predictions and their associated
uncertainties are shown in separate panels for visual clarity.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3.pdf}
\caption{Sensitivity of equilibrium cover to a 1\% increase in
precipitation (+ppt), temperature (+temp), or both (+ppt\&temp) applied
to individual and combined vital rates. For example, the points
associated with G show the median cover from IPM simulations where a
climate perturbation is applied only to the growth regression climate
covariates.}
\end{figure}

>>>>

\section{Do we need detailed demographic data to forecast the impacts of
climate change on plant
populations?}\label{do-we-need-detailed-demographic-data-to-forecast-the-impacts-of-climate-change-on-plant-populations}

@@

Our demographic data comes from the Fort Keogh Livestock and Range
Research Laboratory in eastern Montana's northern mixed prairie near
Miles City, Montana, USA ($46^{\circ}$ 19' N, $105^{\circ}$ 48' W). The
dataset is freely available on Ecological Archives\footnote{\url{http://esapubs.org/archive/ecol/E092/143/}}
(Anderson et al. 2011) , and interested readers should refer to the
metadata therein for a complete description. The site is about 800 m
above sea level and mean annual precipitation (1878-2009) is 334 mm,
with most annual precipitation falling from April through September. The
site is grass dominated and, for the purposes of our study, we focus on
the four most abundant graminoid species: \emph{Bouteloua gracilis}
(BOGR), \emph{Hesperostipa comata} (HECO), \emph{Pascopyrum smithii}
(PASM), and \emph{Poa secunda} (POSE) (Fig. 1).

@@

In this paper, we model populations based on two levels of data:
individual and quadrat (Fig. 2). The individual data is the ``raw''
data. For the quadrat level we data we simply sum individual areal cover
for each quadrat by species. This is equivalent to a perfect census of
quadrat percent cover, so we do not need to consider measurement error.
Based on these two datasets we can compare population models built using
individual level data and aggregated quadrat level data.

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Time series of average percent cover over all quadrats for our
four focal species: \emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa
comata} (HECO), \emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda}
(POSE).}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Work flow of the data aggregation, model fitting, and
population simulating.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3.pdf}
\caption{Proportional change in species' mean cover caused by a 1\%
increase in observed precipitation (+ppt), temperature (+temp), or both
(+ppt\&temp) as predicted by the individual-based IPM and the
aggregate-based QBM. Top panels show the mean predicted proportional
change in cover; lower panels show the 90\% quantiles of predicted
proportional cover change. Mean predictions and their associated
uncertainties are shown in separate panels for visual clarity.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_4.pdf}
\caption{Sensitivity of equilibrium cover to a 1\% increase in
precipitation (+ppt), temperature (+temp), or both (+ppt\&temp) applied
to individual and combined vital rates. For example, the points
associated with G show the median cover from IPM simulations where a
climate perturbation is applied only to the growth regression climate
covariates.}
\end{figure}
